---
title: "Reassigning Node Names"
author: "Ethan Tenison"
date: "5/23/2021"
output: html_document
---

# Reassigning Node Names for Network Analysis

Due privacy concerns, the survey participants' names need to be anonymized. To accomplish this, I row bound all the original network data, and assigned integers to participants. This will ensure that ID's are consistent throughout the analysis and that managers will have a key.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(janitor)
```

```{r raw_files, include=FALSE}

layer1_raw <- read_csv("Layer 1_SAMB/SAMB_cohort_network.csv")
layer2_raw <- read_csv("Layer 2_SAMB plus USFWS partners/USFWS_network_in region.csv")
layer3_raw <- read_csv("Layer 3_SAMB plus External Partners/external_network_clean.csv")

```

## Data Cleaning

First I cleaned the column names using the `Janitor` package and then selected ego and alter. After that I put all egos and alters into one list and kept only the unique values. Finally, I assigned a unique `id` to each survey participant.

```{r data_cleaning}


layer1 <- layer1_raw
layer1 <- layer1 %>% clean_names() %>% select(ego, alter)
all_names <- c(layer1[['ego']], layer1[['alter']])


layer2 <- layer2_raw
layer2 <- layer2 %>% clean_names() %>% select(ego, alter)
all_names <- c(all_names, layer2[['ego']], layer2[['alter']])

layer3 <- layer3_raw
layer3 <- layer3 %>% clean_names() %>% select(ego, alter)
all_names <- c(all_names, layer3[['ego']], layer3[['alter']])


all_names <- unique(all_names)

df <- as.data.frame(all_names)
df <- tibble::rowid_to_column(df, "id")

write.csv(df, "standardized_ids.csv", row.names = FALSE)
```
